On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 bqp.tex
Rephrase discussions and write BlindBQP proof

\Ethan{Read other papers and see if I can copy their tones and phrasing}

\Ethan{Important lemmas such as 2.4 should be emphasized more and especially this one shouldn't be in prelim.}

\Ethan{2.4 should be a key obsv.}

\Ethan{If the original is wordy, just keep it the way it is. Don't try to simplify existing dfns.}

\Ethan{Two main problems; 1. not professional enough, 2. flow}

@@

We start with a high-level description of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which was in turn taken from \cite{mf16}.

\Ethan{below is copied and pasted from google docs and might need a bit of rephrasing}
Thm 8.4 in Urmila's paper gives a one-message $\QPIP_1$ protocol with XZ measurement for deciding BQP language L.
Roughly, on input $x \in\set{0,1}^n$,  P will send a m = poly(n) qubit certificate state $\rho$ to V qubit by qubit.
V will sample a measurement setting $h \in \set{0,1}^m$ according to certain distribution $\pi_x$, and use h to determine how to measure $\rho$.
Specifically, if $h_i = 0$ (resp., 1), then V will measure the i-th qubit using  X (resp., Z) measurement, and verify the measurement outcome.

\begin{protocol}{Verifying yes-instances for $\BQP$}
	\label{proto:BQP}
	Let $L\in\BQP$, and $x\in\set{0,1}^n$. Let $m=\poly(n)$
	\begin{enumerate}
		\item On input $L$ and $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_{L, x}$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is single-qubit $X$ or $Z$ measurements.
		\item The verifier sends $x$ to the prover.
		\item The prover applies a certain CPTP $\cF$ on $x$ to generate $\rho\in\cB^{\otimes m}$.
			\Ethan{Now we need to define CPTP in prelim...}
		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $c$.
		\item The verifier runs some $\BPP$ algorithm $\cV$ on input $c$ and outputs either accept or reject.
	\end{enumerate}
\end{protocol}

\Ethan{below is copied from google docs and need rephrasing}

compile this protocol using QFHE to obtain a blind one message $\QPIP_1$ protocol for BQP with XZ measurement.
High level idea:  run the protocol under Urmila’s QFHE. Namely, $\tilde{V}$ sends $ct = Enc(x)$ to $\tilde{P}$, then $\tilde{P}$ homomorphically evaluate $P_1$ on ct to produce $\tilde{rho} = Enc(\rho)$ and send the encrypted certificate state to $\tilde{V}$.
Discussion: Now $\tilde{V}$ need to obtain the measurement outcome w from the encrypted state $\tilde{rho}$ using qubit-by-qubit XZ measurements. This may not be possible in general. 
Key observation: Our key observation is that Urmila’s QFHE scheme allows this. 
Explain why: Urmila’s QFHE ciphertext has the form of  QOTP on quantum msg + classical FHE ciphertext. So $\tilde{V}$ can do blah blah XZ measurement on $\tilde{rho}$, and recover w from the measurement outcome. We state this as the following fact/key observation: ...

@@

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\Ethan{Define/quantify $x$ and whatnot}
	Let $d$ be the depth of the circuit corresponding to $\cF$.
	Take $\pi_{L, x}$, $\cF$, and $\cV$ to be the same as in \cref{proto:BQP}
	\begin{enumerate}
		\item The verifier samples $\Lambda$ from $\pi_{L, x}$
		\item The verifier computes $\Lambda'$ using \cref{decodeMeasureOrder}
		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
		\item The verifier computes $c=\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c$ and $evk$ to the prover
		\item The prover computes $\sigma=\mathsf{QHE.Eval}(\cF, c)$
		\item The prover sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext according to $\Lambda'$, getting $ct$
		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $c$.
		\item The verifier applies $\cV$ to $c$ and outputs its result.
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\cref{proto:BlindBQP} has negligible completeness and soundness.
\end{thm}
\begin{proof}
    \Ethan{Completeness is trivial, but soundness isn't as trivial as this makes it look like}
	Based on the correctness of $\mathsf{QHE}$, any prover strategy in \cref{proto:BlindBQP} has a corresponding strategy in \cref{proto:BQP}.
\end{proof}

>>>>

\Ethan{TODO Read other papers and see if I can copy their tones and phrasing}

\Ethan{Note to self: If the original is wordy, just keep it the way it is. Don't try to simplify existing dfns.}

@@

We start with a high-level description of the $\QPIP_1$ scheme from \cite{mahadev_delegation}, which is in turn taken from \cite{mf16}.

This is a one-message $\QPIP_1$ protocol with only $X$ and $Z$ measurement for deciding a $\BQP$ language $L$.
Roughly, on input $x\in\set{0,1}^n$, the prover sends a $m$-qubit certificate state $\rho$ to the verifier qubit-by-qubit.
The verifier samples a product measurement $\Lambda$ of $X$ and $Z$s according to certain distribution to apply to $\rho$
The verifier then, using the measurement results, decides whether to accept or reject.

\begin{protocol}{1-message $\QPIP_1$ protocol for $\BQP$}
	\label{proto:BQP}
	Let $L\in\BQP$, and $x\in\set{0,1}^n$. Let $m=\poly(n)$
	\begin{enumerate}
		\item On input $L$ and $x$, the verifier samples $\Lambda$ from a certain distribution $\pi_{L, x}$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is single-qubit $X$ or $Z$ measurements.
		\item The verifier sends $x$ to the prover.
		\item The prover applies a certain CPTP $\cF$ on $x$ to generate $\rho\in\cB^{\otimes m}$.
			\Ethan{Now we need to define CPTP in prelim...}
		\item The prover sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming qubits of $\rho$ according to $\Lambda$ to get $w$.
		\item The verifier runs some $\BPP$ algorithm $\cV$ on input $w$ and outputs either accept or reject.
	\end{enumerate}
\end{protocol}

We compile this protocol using $\mathsf{QHE}$ to obtain a blind 1-message $\QPIP_1$ protocol for $\BQP$, again with only $X$ and $Z$ measurements.
The high level idea is to run \cref{proto:BQP} under $\mathsf{QHE}$.
Namely, the verifier encrypts its original input $x$ and sends $y=\mathsf{QHE.Enc}(x)$ to the prover.
The prover then homomorphically evaluate $\cF$ on $y$ to produce $\sigma=\mathsf{QHE.Enc}(\rho)$ \Ethan{Is this actually ok? $\sigma$ is a ciphertext corresponding to $\rho$, but it wasn't encrypted. In fact it's deteriorated due to homomorphic eval} and send it back to the verifier.

Now the verifier needs to obtain the measurement outcome $w$ from the encrypted state $\sigma$ using qubit-by-qubit $X$ and $Z$ measurements.
This may not be possible in general, but we observe that $\mathsf{QHE}$ allows this. 
Its ciphertexts consists of a Pauli one-time-padded plaintext and classically encrypted Pauli keys.
Pauli one-time-pads commute with $X$ and $Z$ measurements, so the verifier can measure the one-time-padded state as usual then correct the measurement results using the Pauli keys.
We state this observation as the following theorem:

@@

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $x\in\set{0,1}^n$.
	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cF$.
	Take $\pi_{L, x}$, $\cF$, and $\cV$ to be the same as in \cref{proto:BQP}
	\begin{enumerate}
		\item The verifier samples $\Lambda$ from $\pi_{L, x}$
		\item The verifier computes $\Lambda'$ using \cref{decodeMeasureOrder}
		\item The verifier runs $\mathsf{QHE.Keygen}(1^n, 1^d)$ to get $pk, sk, evk$.
		\item The verifier computes $y=\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $y$ and $evk$ to the prover
		\item The prover computes $\sigma=\mathsf{QHE.Eval}(\cF, y)$
		\item The prover sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier measures the incoming ciphertext according to $\Lambda'$, getting $ct$
		\item The verifier applies $\widehat{\mathsf{QHE.Dec}_{sk}}$ to $ct$, getting $w$.
		\item The verifier applies $\cV$ to $w$ and outputs its result.
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\cref{proto:BlindBQP} has negligible completeness and soundness.
\end{thm}
\begin{proof}
	The completeness follows by inspection.

	For soundness, suppose the prover sends $\sigma$.

	The verifier's actions, by \cref{decodeMeasureOrder}, is $\negl(n)$-close to to decoding $\sigma$ to get some $\rho$ then applying $\Lambda$ to get $w$.
	In other words, the verifier's outputs is $\negl(n)$-close to the verifer of \cref{proto:BQP} under the same input and receiving $\rho$ from the prover.
	So the conclusion follows from the negligible soundness of \cref{proto:BQP}.
\end{proof}
